---
title: "Task 1"
author: "Mikhail Zhilkin"
date: "`r Sys.Date()`"
output: html_notebook
---

```{r}
library(scales)
library(tidyverse)
```

&nbsp;

Import the data set:

```{r}
df <- readxl::read_excel(
	"Task11part-2hr30mins.xlsx",
	range = cell_cols("A:D")
)
```

```{r}
head(df)
```

&nbsp;

Distribution of players across groups looks fine:

```{r}
df %>% 
	count(Country, Group) %>% 
	spread(Country, n)
```

&nbsp;

Gross revenue per player would indicate that Group 3 ($25 bonus) performed best:

```{r fig.width=10}
df %>% 
	mutate(GrossRev = Activity * .0213) %>% 
	group_by(Group) %>% 
	summarise(mean(GrossRev)) %>% 
	ggplot() +
		geom_col(aes(ordered(Group), `mean(GrossRev)`), alpha = .5) +
		labs(x = "Group", y = "") +
		scale_y_continuous(labels = dollar_format())
```

&nbsp;

Net revenue (gross revenue minus bonus) gives victory by a slim margin to Group 4 ($5 bonus):

```{r fig.width=10}
df %>% 
	mutate(
		GrossRev = Activity * .0213,
		NetRev = GrossRev - c(20, 15, 25, 5, 0)[Group]
	) %>% 
	group_by(Group) %>% 
	summarise(mean(GrossRev), mean(NetRev)) %>% 
	ggplot() +
		geom_col(aes(ordered(Group), `mean(GrossRev)`), alpha = .5) +
		geom_col(aes(ordered(Group), `mean(NetRev)`), alpha = .5) +
		labs(x = "Group", y = "") +
		scale_y_continuous(labels = dollar_format())
```

&nbsp;

Different results in different countries suggest that things are more complicated, with no group winning across the board:

```{r fig.width=10}
df %>% 
	mutate(NetRev = Activity * .0213 - c(20, 15, 25, 5, 0)[Group]) %>% 
	group_by(Country, Group) %>% 
	summarise(mean(NetRev)) %>% 
	ggplot() +
		facet_wrap(~Country) +
		geom_col(aes(ordered(Group), `mean(NetRev)`), alpha = .5) +
		labs(x = "Group", y = "") +
		scale_y_continuous(labels = dollar_format())
```

&nbsp;

Distribution of net revenue is extremely uneven, with `r sprintf("%.1f%%", df %>% mutate(NetRev = Activity * .0213 - c(20, 15, 25, 5, 0)[Group]) %>% arrange(-NetRev) %>% transmute(x = row_number() / n(), y = cumsum(NetRev) / sum(NetRev)) %>% filter(y >= .8) %>% head(1) %>% pull(x) %>% '*' (100))` of top spenders responsible for 80% of it (the downward bend is due to players with *negative* net revenue):

```{r fig.width=10}
df %>% 
	mutate(NetRev = Activity * .0213 - c(20, 15, 25, 5, 0)[Group]) %>% 
	arrange(-NetRev) %>% 
	transmute(x = row_number() / n(), y = cumsum(NetRev) / sum(NetRev)) %>% 
	ggplot() +
		geom_line(aes(x, y)) +
		labs(x = "Players", y = "Net Revenue") +
		scale_x_continuous(labels = percent_format()) +
		scale_y_continuous(labels = percent_format())
```

&nbsp;

Let's calculate 95% confidence interval for net revenue per player for each Country/Group using [bootstrapping](https://en.wikipedia.org/wiki/Bootstrapping_(statistics)):

```{r}
tmp <- expand.grid(
	Country = unique(df$Country),
	Group = unique(df$Group),
	stringsAsFactors = FALSE
)
```

```{r}
df2 <- do.call(
	rbind,
	mapply(
		function(a, b) {
			x <- df %>% filter(Country == a, Group == b) %>% pull(Activity)
			
			y <- quantile(
				replicate(1e+4, { mean(sample(x, length(x), replace = TRUE)) }),
				c(.05, .95)
			)
			
			tibble(
				Country = a,
				Group = b,
				Lower = y[1] * .0213 - c(20, 15, 25, 5, 0)[b],
				Upper = y[2] * .0213 - c(20, 15, 25, 5, 0)[b]
			)
		},
		tmp$Country,
		tmp$Group,
		SIMPLIFY = FALSE
	)
)
```

&nbsp;

Swains Island appears to be the only market with a clear indication that the campaign has been beneficial, with control group falling behind. Otherwise, one cannot draw conclusions from the data available:

```{r fig.width=10, message=FALSE}
df %>% 
	mutate(NetRev = Activity * .0213 - c(20, 15, 25, 5, 0)[Group]) %>% 
	group_by(Country, Group) %>% 
	summarise(mean(NetRev)) %>% 
	inner_join(df2) %>% 
	ggplot() +
		facet_wrap(~Country) +
		geom_col(aes(ordered(Group), `mean(NetRev)`), alpha = .5) +
		geom_segment(aes(
			x = ordered(Group),
			xend = ordered(Group),
			y = Lower,
			yend = Upper
		)) +
		labs(x = "Group", y = "") +
		scale_y_continuous(labels = dollar_format())
```

&nbsp;

Suggestions for future analysis & research:

* Identify biggest spenders and remove them from this kind of analysis, which may result in more narrow confidence intervals. (This is based on a risky assumption that high spenders' behaviour isn't affected by a small bonus.)
* Segment players based on their pre-test behaviour (e.g. low/medium/high spenders) and analyse the impact of bonus campaign on each segment separately.
* If possible, test campaign on a larger number of users.

&nbsp;
