---
title: "Task 2"
author: "Mikhail Zhilkin"
date: "`r Sys.Date()`"
output: html_notebook
---

```{r}
library(scales)
library(tidyverse)
```

```{r, include=FALSE}
Sys.setlocale("LC_ALL","English")
```

&nbsp;

Import the data set:

```{r}
dailyplay <- readxl::read_excel("Task22parts-2hr30mins[1].xlsx", sheet = 1)
promotions <- readxl::read_excel("Task22parts-2hr30mins[1].xlsx", sheet = 2)
```

&nbsp;

Aggregated data:

```{r, message=FALSE}
df <- dailyplay %>% 
	group_by(Date) %>% 
	summarise(Players = n(), Revenue = sum(Revenue)) %>% 
	inner_join(promotions) %>% 
	mutate(
		Dayofweek = weekdays(Date),
		Promo = ifelse(is.na(Promo), " ", Promo)
	)
```

```{r}
df
```

&nbsp;

Simple linear regression model:

```{r}
fit <- df %>% lm(Revenue ~ Dayofweek + Promo + Players, .)
```

```{r}
summary(fit)
```

&nbsp;

**a. What is the predicted revenue for the below days?**

```{r}
a <- tibble(
	Dayofweek = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"),
	Promo = c(" ", "A", " ", "B", "A", "B", " "),
	Players = c(3, 4, 4, 5, 6, 6, 7) * 1000
)
```

```{r}
cbind(a, predict.lm(fit, a))
```

&nbsp;

**b. Which promotion do you think performs better and why?**

From the model summary above, it's clear that Promo B has a significantly higher positive impact on revenue. This can easily be verified by predicting revenue for Promo A and Promo B with everything else being equal. Indeed, prediction for Promo B is much higher:

```{r}
predict.lm(
	fit,
	tibble(
		Dayofweek = rep("Monday", 2),
		Promo = c("A", "B"),
		Players = rep(1000, 2)
	)
)
```

&nbsp;

**c. What are the 95% confidence intervals to your revenue predictions?**

Last two columns contain lower/upper bounds of the confidence interval at the default level of 95%:

```{r}
cbind(a, predict.lm(fit, a, interval = "confidence"))
```

&nbsp;

**d. Plot the residuals and explain what they tell us about the model**

Residuals look reasonably random, although the model appears to overestimate revenue on 'bad' days and, to some extent, very good ones, too:

```{r fig.width=10}
plot(fit, which = 1)
```

&nbsp;

We can achieve better results with a slightly more sophisticated model:

```{r}
fit2 <- df %>% lm(Revenue ~ Dayofweek * Promo * Players + 0, .)
```

```{r fig.width=10}
plot(fit2, which = 1)
```

&nbsp;

**e. With more time and data would you approach this problem differently?**

Things I'd consider doing:

* Take a close look at outliers --- days for which prediction is way off. Can they be explained? Do they suggest any variables we might want to include in the model?

* Player segmentation (e.g. low/medium/ high spenders) --- as another variable in the model, or even separate model for each segment.

* In addition to the promo running on a given day, take into account promotional activity *prior* to that day. The impact of the first day of a promotion campaign can be quite different from that of day 5.

&nbsp;
